Review of Assigned Readings

### 2018-01-04 paper/paper.tex

\subsection{Research Question and Goal of the Paper}
\label{sec:ResearchQandGoal}
As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount of bitcoin topics on Twitter. The goal should be reached by answering the following research question: \\
To what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?

>>>>

\subsection{Research Question and Goal of the Paper}
\label{sec:ResearchQandGoal}

As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter. The goal should be reached by answering the following research question: \\
In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
